\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-02-21 doc/paper.tex
extend the boundary conditions section

\subsection{Boundary conditions}
In \fs the RGE boundary conditions are implemented by inheriting from
a common \code{Constraint<Two\_scale>} interface class and
implementing the pure virtual functions \code{apply()},
\code{get\_scale()} and \code{set\_model()}, see
\figurename~\ref{fig:schematic-two-scale-constraint-interface}.  Per
default, \fs creates three default boundary conditions:
%
\begin{itemize}
\item \emph{GUT constraint:} Here the \code{apply()} function
  calculates the value of the unification scale $M_X$ (from the
  condition given in \code{HighScale}) and sets the model parameters
  given in \code{HighScaleInput}.
\item \emph{SUSY constraint:} Here the \code{apply()} function
  calculates the value of the susy scale $M_S$ and sets the model
  parameters given in \code{SUSYScaleInput}.  Afterwards the EWSB
  conditions are solved for the parameters given in
  \code{EWSBOutputParameters} at the one-loop level, i.e., the the
  parameters in \code{EWSBOutputParameters} are determined such that
  the one-loop effective potential is minimized.
\item \emph{Low-scale constraint:} This constraint matches the gauge
  and Yukawa couplings of the susy model to the Standard Model values
  using threshold corrections.  Furthermore the parameters given in
  \code{LowScaleInput} are set.
\end{itemize}

>>>>

\subsection{Boundary conditions}
In \fs the RGE boundary conditions are classes which implement
\code{Constraint<Two\_scale>} interface, see
\figurename~\ref{fig:schematic-two-scale-constraint-interface}.
%
\begin{lstlisting}[language=C++]
template<>
class Constraint<Two_scale> {
public:
   virtual ~Constraint() {}
   virtual void apply() = 0;
   virtual double get_scale() const = 0;
   virtual void set_model(Two_scale_model*) = 0;
};
\end{lstlisting}
%
The three pure virtual functions \code{apply()}, \code{get\_scale()}
and \code{set\_model()} need to be implemented
%
\begin{itemize}
\item \code{apply()}: implements the constraint by fixing model
  parameters
\item \code{get\_scale()}: returns the scale at which the constraint
  is to be applied.
\item \code{set\_model()}: connects the constraint to a model class,
  in order to access the model parameters
\end{itemize}
%
Per default, \fs creates three default boundary conditions for each
model:
%
\begin{itemize}
\item \emph{GUT constraint:} Here the \code{apply()} function
  calculates the value of the unification scale $M_X$ (from the
  condition given in \code{HighScale}) and sets the model parameters
  given in \code{HighScaleInput}.  The \code{get\_scale()} returns the
  value of $M_X$.
\item \emph{SUSY constraint:} Here the \code{apply()} function
  calculates the value of the susy scale $M_S$ and sets the model
  parameters given in \code{SUSYScaleInput}.  Afterwards the EWSB
  conditions are solved for the parameters given in
  \code{EWSBOutputParameters} at the one-loop level, i.e., the the
  parameters in \code{EWSBOutputParameters} are determined such that
  the one-loop effective potential is minimized.  The
  \code{get\_scale()} returns the value of $M_S$.
\item \emph{Low-scale constraint:} This constraint calculates the
  gauge and Yukawa couplings of the susy model from the known Standard
  Model gauge couplings and fermion masses (at $M_Z$), using threshold
  corrections.  Furthermore the parameters given in
  \code{LowScaleInput} are set.  The \code{get\_scale()} returns the
  value of $M_Z$.
\end{itemize}
